Hidden Talents in Context: Multiverse analysis repository

### 2022-04-05 manuscript/manuscript.Rmd
fix figure captions in manuscript

```{r figure2, fig.path="figures/", dev="pdf", fig.id = "figure2", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap = "Visualization of multiverse attention shifting results. Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure (y-axis was reversed so that higher values = faster shifting), b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect."}
fig2
```

@@

```{r figure3, fig.path="figures/", dev="pdf", fig.id = "figure3", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap="Visualization of multiverse working memory updating results. Specifically, a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure, b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect. Proportions of each arbitrary decision with p-values < .05 are indicated on the right side of each specification grid. Blank proportions indicate proportions = 0. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
fig3
```

>>>>

```{r figure2, fig.path="figures/", dev="pdf", fig.id = "figure2", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap = "Visualization of multiverse attention shifting results. Unpredictability and violence exposure multiverse analyses were confirmatory and poverty analyses were exploratory. a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure (y-axis was reversed so that higher values = faster shifting), b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect."}
fig2
```

@@

```{r figure3, fig.path="figures/", dev="pdf", fig.id = "figure3", fig.cap.style = "Image Caption", fig.width=6.5, fig.height=7.25, dpi=600, fig.cap="Visualization of multiverse working memory updating results. Unpredictability and violence exposure multiverse analyses were confirmatory and poverty analyses were exploratory. a) visualizes the multiverse task version × adversity interaction on abstract and ecological task versions across high (+ 1 SD) and low (- 1 SD) adversity exposure, b) plots p-curves associated with each interaction term, c) plots sorted interaction B-coefficients across each arbitrary decision, d) plots the sample sizes for each effect, and e) is a specification grid indicating the data processing decisions associated with each effect. Proportions of each arbitrary decision with p-values < .05 are indicated on the right side of each specification grid. Blank proportions indicate proportions = 0. Teal lines and points reflect individual multiverse effect sizes with p-values < .05."}
fig3
```
